Flowchart of Current Algorithm

### 2009-05-04 docs/flowchart/flowchart.tex
setting (rho h)_0^n = avg((rho h)^{(1)}) in step 4 rather than step 3 - makes more sense in the flow of the alg.  no changes to results
another simplification - moved computation of gamma1bar^{(1)} from step 3 into step 4, and only do it if you are in spherical since it's not used in plane-parallel.  flow chart reads better.  no changes to results
minor

The local velocity field is described by paper III equation (37),
\begin{equation}
\frac{\partial\Ubt}{\partial t} = - \Ubt \cdotb \nablab \Ubt - w_0 \frac{\partial \Ubt}{\partial r}
                                 - \left(\Ubt \cdotb \er\right) \frac{\partial w_0}{\partial r} \er
                                 - \frac{1}{\rho} \nablab\pi
                                 + \frac{1}{\rho_0} \frac{\partial \pizero}{\partial r} \er
                                 - \frac{(\rho-\rhozero)}{\rho} \; g \; \er  \label{eq:utildeupd}  \enskip\
 .
\end{equation}

We construct time-centered velocities at edges, $\uadvone$, 
using a second-order unsplit Godunov procedure, as described
in Appendix B of paper III.  We note that  $\uadvone$ satisfies 
the discrete versions of paper III equation (21),
\begin{equation}
\int_{\Omega_H} \Ubt \cdotb \er \; dA = 0 \label{eq:udoterzero} \enskip ,
\end{equation}
and paper III equation (39),
\begin{equation}
\nablab \cdotb (\beta_0 \Ubt )  = \beta_0 \left(S - \Sbar \right )\enskip ,
\label{eq:tildeconstraint}
\end{equation}
with the discretization
\begin{equation}
\nablab \cdotb \left(\beta_0^n \uadvone\right) = 
\beta_0^n \left(S^{\nph,\star} - \overline{S^{\nph,\star}}\right) \enskip .
\end{equation}
The discretization with the volume discrepancy correction is
\begin{equation}
\nablab \cdotb \left(\beta_0^n \uadvone\right) = 
\beta_0^n \left\{ \left(S^{\nph,\star} - \overline{S^{\nph,\star}}\right)
+ \frac{f}{\gammabar^n p_0^n}
\left[\frac{p(\rho,h,X_k)^n - \overline{p(\rho,h,X_k)^n}}{\Delta t^n}\right]\right\} \enskip .
\end{equation}

@@

\item {\bf React State}$[\rho^n, (\rho h)^n, X_k^n, T^n, (\rho\Hext)^n, p_0^n]
                   \rightarrow$ $[ \rho^{(1)}, (\rho h)^{(1)}, X_k^{(1)}, T^{(1)},
                                  (\rho \omegadot_k)^{(1)}, (\rho \Hnuc)^{(1)} ].$

\item Define
\begin{equation}
\gammabar^{(1)} = {\rm{\bf Avg}} \left[ \Gamma_1\left(\rho^{(1)}, p_0^{n}, X_k^{(1)}\right) \right] \enskip .
\end{equation}

@@

\item Compute $\psi$.
\begin{description}
\item For plane-parallel, 
\begin{equation}
\psi_j^{n+\myhalf,\star} = \frac{1}{2} \left(\eta_{\rho,j-\myhalf}^{n+\myhalf,\star} 
+ \eta_{\rho,j+\myhalf}^{n+\myhalf,\star}\right) g^{n+1,\star} \enskip .
\end{equation}
\item For spherical, first compute:
\begin{equation}
\gammabar^{(2)} = {\rm{\bf Avg}} \left[ \Gamma_1\left(\rho^{(2)}, p_0^{n+1,\star}, 
X_k^{(2)}\right) \right] \enskip .
\end{equation}
Then, define a base time and time-centered $\psi$:
\begin{equation}
\psi_j^{n,\star} = 
\left(\gammabar^{(1)} p_0^n\right)_j
\left \{ \Sbar_j^{n+\myhalf,\star} - 
\frac{1}{r_j^2} \left [ (r^2 w_0^{n+\myhalf,\star})_{j+\myhalf} -
          (r^2 w_0^{n+\myhalf,\star})_{j-\myhalf} \right ] \right \} \enskip ,
\end{equation}
\begin{eqnarray}
\psi_j^{n+\myhalf,\star} &=& 
\left(\frac{\gammabar^{(1)}+\gammabar^{(2)}}{2}\right)_j
\left(\frac{p_0^n+p_0^{n+1,\star}}{2}\right)_j \nonumber \\
&& \left \{ \Sbar_j^{n+\myhalf,\star} - 
\frac{1}{r_j^2} \left [ (r^2 w_0^{n+\myhalf,\star})_{j+\myhalf} -
          (r^2 w_0^{n+\myhalf,\star})_{j-\myhalf} \right ] \right \} \enskip .
\end{eqnarray}
\end{description}

@@

\item Compute $\psi$.
\begin{description}
\item For plane-parallel, 
\begin{equation}
\psi_j^{n+\myhalf} = \frac{1}{2} \left(\eta_{\rho,j-\myhalf}^{n+\myhalf} 
+ \eta_{\rho,j+\myhalf}^{n+\myhalf}\right) g^{n+1} \enskip .
\end{equation}
\item For spherical, first compute:
\begin{equation}
\gammabar^{(2),\star} = {\rm{\bf Avg}} \left[ \Gamma_1\left(\rho^{(2),\star}, p_0^{n+1}, 
X_k^{(2),\star}\right) \right] \enskip .
\end{equation}
Then, define a base time and time-centered $\psi$:
\begin{equation}
\psi_j^{n} = 
\left(\gammabar^{(1)} p_0^n\right)_j
\left \{ \Sbar_j^{n+\myhalf} - 
\frac{1}{r_j^2} \left [ (r^2 w_0^{n+\myhalf})_{j+\myhalf} -
          (r^2 w_0^{n+\myhalf})_{j-\myhalf} \right ] \right \} \enskip ,
\end{equation}
\begin{eqnarray}
\psi_j^{n+\myhalf} &=& 
\left(\frac{\gammabar^{(1)}+\gammabar^{(2),\star}}{2}\right)_j
\left(\frac{p_0^n+p_0^{n+1}}{2}\right)_j \nonumber \\
&& \left \{ \Sbar_j^{n+\myhalf} - 
\frac{1}{r_j^2} \left [ (r^2 w_0^{n+\myhalf})_{j+\myhalf} -
          (r^2 w_0^{n+\myhalf})_{j-\myhalf} \right ] \right \} \enskip .
\end{eqnarray}
\end{description}

>>>>

The local velocity field is described by paper III equation (37),
\begin{equation}
\frac{\partial\Ubt}{\partial t} = 
- \left(\Ubt+w_0\right) \cdotb \nablab \Ubt
- \left(\Ubt \cdotb \er\right) \frac{\partial w_0}{\partial r} \er
- \frac{1}{\rho} \nablab\pi
+ \frac{1}{\rho_0} \frac{\partial \pizero}{\partial r} \er
- \frac{(\rho-\rhozero)}{\rho} \; g \; \er  \label{eq:utildeupd}  \enskip .
\end{equation}

We construct time-centered velocities at edges, $\uadvone$, 
using a second-order unsplit Godunov procedure followed by an elliptic
solve, as described in Appendix B of paper III.  We note that 
$\uadvone$ satisfies the discrete versions of paper III equation (21),
\begin{equation}
\int_{\Omega_H} \Ubt \cdotb \er \; dA = 0 \label{eq:udoterzero} \enskip ,
\end{equation}
and paper III equation (39),
\begin{equation}
\nablab \cdotb (\beta_0 \Ubt )  = \beta_0 \left(S - \Sbar \right )\enskip ,
\label{eq:tildeconstraint}
\end{equation}
with the discretization
\begin{equation}
\nablab \cdotb \left(\beta_0^n \uadvone\right) = 
\beta_0^n \left(S^{\nph,\star} - \overline{S^{\nph,\star}}\right) \enskip .
\end{equation}
The discretization with the volume discrepancy correction is
\begin{equation}
\nablab \cdotb \left(\beta_0^n \uadvone\right) = 
\beta_0^n \left\{ \left(S^{\nph,\star} - \overline{S^{\nph,\star}}\right)
+ \frac{f}{\gammabar^n p_0^n}
\left[\frac{p(\rho,h,X_k)^n - \overline{p(\rho,h,X_k)^n}}{\Delta t^n}\right]\right\} \enskip .
\end{equation}

@@

{\bf React State}$[\rho^n, (\rho h)^n, X_k^n, T^n, (\rho\Hext)^n, p_0^n] \rightarrow
[ \rho^{(1)},(\rho h)^{(1)},X_k^{(1)},T^{(1)},(\rho \omegadot_k)^{(1)},(\rho \Hnuc)^{(1)} ]$.

@@

\item Compute $\psi$.
\begin{description}
\item For plane-parallel, 
\begin{equation}
\psi_j^{n+\myhalf,\star} = \frac{1}{2} \left(\eta_{\rho,j-\myhalf}^{n+\myhalf,\star} 
+ \eta_{\rho,j+\myhalf}^{n+\myhalf,\star}\right) g^{n+1,\star} \enskip .
\end{equation}
\item For spherical, first compute:
\begin{equation}
\gammabar^{(1)} = {\rm{\bf Avg}} \left[ \Gamma_1\left(\rho^{(1)}, p_0^{n}, 
X_k^{(1)}\right) \right] \enskip ,
\end{equation}
\begin{equation}
\gammabar^{(2),\star} = {\rm{\bf Avg}} \left[ \Gamma_1\left(\rho^{(2),\star}, p_0^{n+1,\star}, 
X_k^{(2),\star}\right) \right] \enskip .
\end{equation}
Then, define a base time and time-centered $\psi$:
\begin{equation}
\psi_j^{n,\star} = 
\left(\gammabar^{(1)} p_0^n\right)_j
\left \{ \Sbar_j^{n+\myhalf,\star} - 
\frac{1}{r_j^2} \left [ (r^2 w_0^{n+\myhalf,\star})_{j+\myhalf} -
          (r^2 w_0^{n+\myhalf,\star})_{j-\myhalf} \right ] \right \} \enskip ,
\end{equation}
\begin{eqnarray}
\psi_j^{n+\myhalf,\star} &=& 
\left(\frac{\gammabar^{(1)}+\gammabar^{(2),\star}}{2}\right)_j
\left(\frac{p_0^n+p_0^{n+1,\star}}{2}\right)_j \nonumber \\
&& \left \{ \Sbar_j^{n+\myhalf,\star} - 
\frac{1}{r_j^2} \left [ (r^2 w_0^{n+\myhalf,\star})_{j+\myhalf} -
          (r^2 w_0^{n+\myhalf,\star})_{j-\myhalf} \right ] \right \} \enskip .
\end{eqnarray}
\end{description}

@@

\item Compute $\psi$.
\begin{description}
\item For plane-parallel, 
\begin{equation}
\psi_j^{n+\myhalf} = \frac{1}{2} \left(\eta_{\rho,j-\myhalf}^{n+\myhalf} 
+ \eta_{\rho,j+\myhalf}^{n+\myhalf}\right) g^{n+1} \enskip .
\end{equation}
\item For spherical, first compute:
\begin{equation}
\gammabar^{(2)} = {\rm{\bf Avg}} \left[ \Gamma_1\left(\rho^{(2)}, p_0^{n+1}, 
X_k^{(2)}\right) \right] \enskip .
\end{equation}
Then, define a base time and time-centered $\psi$:
\begin{equation}
\psi_j^{n} = 
\left(\gammabar^{(1)} p_0^n\right)_j
\left \{ \Sbar_j^{n+\myhalf} - 
\frac{1}{r_j^2} \left [ (r^2 w_0^{n+\myhalf})_{j+\myhalf} -
          (r^2 w_0^{n+\myhalf})_{j-\myhalf} \right ] \right \} \enskip ,
\end{equation}
\begin{eqnarray}
\psi_j^{n+\myhalf} &=& 
\left(\frac{\gammabar^{(1)}+\gammabar^{(2)}}{2}\right)_j
\left(\frac{p_0^n+p_0^{n+1}}{2}\right)_j \nonumber \\
&& \left \{ \Sbar_j^{n+\myhalf} - 
\frac{1}{r_j^2} \left [ (r^2 w_0^{n+\myhalf})_{j+\myhalf} -
          (r^2 w_0^{n+\myhalf})_{j-\myhalf} \right ] \right \} \enskip .
\end{eqnarray}
\end{description}
